Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-07-26 main-sketch.tex
bettered english
fix abstract

\documentclass[sigconf, anonymous]{acmart}

@@

\begin{document}
\title{Towards a probability measure approach for Differential Privacy in Bayesian inference} % TODO: replace with your title
\subtitle{Extended Abstract}
\begin{abstract}
Bayesian inference is a statistical method which allows to derive a
\emph{posterior} distribution over a parameter, starting from a
\emph{prior} distribution and observed data.  In a setting where the
data must be protected, different approaches have been taken to make
this process differentially private. \citet{dimitrakakis2014robust},
and \citet{wang2015privacy}, for instance, proved that, under specific
conditions, sampling from the posterior distribution is already
differentially private. Other works,
e.g. \cite{zhang2016differential}, \cite{foulds2016theory}, designed
differentially private mechanisms that output a representation of the
full posterior distribution. Also, accuracy of the mechanisms was
measured using metrics on the space of the numeric parameters of the
posterior distribution, e.g. $\ell_1$-norm.

In this work we present a new differentially private algorithm to
compute the posterior in a Beta-Binomial system and in Dirichlet-Multinomial system.
The noise is calibrated w.r.t. a smooth
sensitivity computed with a metric on probability distributions; we
measured the accuracy of the process by using a metric over
probability measures. We compared the accuracy of this approach with
the ones based on $\ell_1$-norm. Experimental results show that when
the data size is small or when the parameters of the prior
distribution are large, the former outperforms the latter.

@@

\noindent In the following whiskers-plots, the y-axis shows the accuracy (or equivalently, the error) of the mechanisms.
Accuracy is measured using Hellinger distance. The x-axis, instead shows  one of the previously mentioned
independent variables --or a combination thereof.
The boxes extend from the lower to the upper quartile values of the data, with a line at the median. A notch on the box around the median
is also drawn to give a rough guide to the significance of difference of medians;
The whiskers extend from the box to show the range of the data. 
A blue box in the plots represents the exponential mechanism behaviour,
while the yellow box next to it represents the performance of a variation of the
basic Laplace mechanism presented in Section (\ref{sec:base}) with the same settings: that is $\epsilon, \delta$, data, prior.
The variation considered performs a post processing on the released parameters so that they
are consistent. For instance in the case when noise is greater than $n$ we will truncate to $n$ to rule out invalid values.
\paragraph{Increasing data size with balanced datasets}
\label{subsubsec_vs_datasize}

>>>>

\documentclass[sigconf]{acmart}

@@

\begin{document}
\title{Tailoring Differentially Private Bayesian Inference to Distance Between Distributions}%Towards a probability measure approach for Differential Privacy in Bayesian inference} % TODO: replace with your title
\subtitle{Extended Abstract}
\begin{abstract}
Bayesian inference is a statistical method which allows one to derive a
\emph{posterior} distribution over a parameter, starting from a
\emph{prior} distribution and observed data.  Settings where sensitive individual information is , different approaches have been taken to make
this process differentially private. \citet{dimitrakakis2014robust},
and \citet{wang2015privacy}, for instance, proved that, under specific
conditions, sampling from the posterior distribution is already
differentially private. Other works,
e.g., \cite{zhang2016differential}, \cite{foulds2016theory}, designed
differentially private mechanisms that output a representation of the
full posterior distribution. Also, accuracy of these mechanisms was
measured using metrics on the space of the numeric parameters of the
posterior distribution, e.g., the $\ell_1$-norm.

In this work we present a new differentially private algorithm to
compute the posterior in a Beta-Binomial system and in a Dirichlet-Multinomial system.
We apply the exponential mechanism to the smooth sensitivity of a metric on probability distributions; we measured the accuracy of the process by using the same metric. We compared the accuracy of this approach with the ones based on $\ell_1$-norm. Experimental results show that when the data size is small or when the parameters of the prior distribution are large, the former outperforms the latter.

@@

\noindent In the following whiskers-plots, the y-axis shows the accuracy (or equivalently, the error) of the mechanisms.
Accuracy is measured using Hellinger distance. The x-axis, instead shows  one of the previously mentioned
independent variables --or a combination thereof.
The boxes extend from the lower to the upper quartile values of the data, with a line at the median. A notch on the box around the median
is also drawn to give a rough guide to the significance of difference of medians;
The whiskers extend from the box to show the range of the data. 
A blue box in the plots represents the exponential mechanism behaviour,
while the yellow box next to it represents the performance of a variation of the
basic Laplace mechanism presented in Section (\ref{sec:base}) with the same settings: that is $\epsilon, \delta$, data, prior.
The variation considered performs a post processing on the released parameters so that they
are consistent. For instance  when  the sum of the noised parameters is greater than $n$ we will truncate them so that they sum up to $n$.
\paragraph{Increasing data size with balanced datasets}
\label{subsubsec_vs_datasize}
